Bayesian Deep Gaussian Processes for Correlated Functional Data: \\ A Case Study in Cosmological Power Spectra

### 2025-05-02 paper/main.tex
update draft, add script P to images

\begin{figure}[ht]
    \centering
    \includegraphics[width=\linewidth, trim=0 13 0 45, clip=TRUE]{plot_data.png}
    \caption{{\it Left:} The perturbation theory (solid green), low resolution runs (solid grey), 
    and high resolution run  (solid pink) for a particular cosmology. 
    The weighted average of these is shown in dashed orange. Dotted lines at the bottom 
    indicate where each data type is deemed approximately unbiased. 
    {\it Middle:} Same as left, but restricted to wavenumber ($k$) values where the low resolution 
    runs are approximately unbiased.
    {\it Right:} Same as left, but with estimated posterior mean subtracted.
    \textcolor{red}{Rerun on Windows for $\mathcal{P}$.  Make axis/labels and legend 
    a bit larger so they are easier to read.  Am I tripping or are the horizontal lines
    in the left panel not lined up correctly?}}
    \label{fig:plot_data}
\end{figure}

These spectra are represented as a function of wavenumber $k$.  Following 
\cite{moran2023mira}, we model on the emulation space 
$\mathcal{P}(k)=\log_{10}\left(\frac{k^{1.5}P(k)}{2\pi^2}\right)$, where $P(k)$ represents the
original spectra. Output is available for $n=351$ values of $k$, spanning
$0.001 \leq k \leq 5$, but each data type has unique wavenumber ranges
where it is deemed approximately unbiased. For $k<0.04$, only $y_p$ provides a reliable 
estimate of the true spectra. $y_{\ell_r}$ are valid for $0.04 \leq k \leq 0.25$, and 
$y_h$ is valid for $0.04 \leq k \leq 5$.  Figure \ref{fig:plot_data} shows an example 
of the output for a particular cosmology. When we focus on $k$ values where $y_{\ell_r}$ 
is valid (center panel), we see each low-resolution and the high-resolution run oscillate around 
a mean term, which is relatively smooth, compared to these realizations. When this
mean term is subtracted, we will obtain a plot like the right panel in 
Figure \ref{fig:plot_data} \textcolor{red}{(This plot goes back to the original range,
would it be prettier and easier for the reader to follow if we kept it to the 
range of the middle panel here?)}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{CAMB_fit_model1.jpg}
    \caption{Example of DGP.HM model fit for the first batch of model runs from the CAMB data, 
             with LOESS mean term subtracted. We can compare the orange lines 
             (posterior mean and dotted 95\% credible interval) to the light blue line,
             representing the infinite-resolution ``true" spectrum.}   
    \label{fig:fit_camb}
\end{figure}

>>>>

% after \linewidth:, trim=0 13 0 45, clip=TRUE
\begin{figure}[ht]
    \centering 
    \includegraphics[width=\linewidth]{plot_data.png}
    \caption{{\it Left:} The perturbation theory (solid green), low resolution runs (solid grey), 
    and high resolution run  (solid pink) for a particular cosmology. 
    The weighted average of these is shown in dashed orange. Dotted lines at the bottom 
    indicate where each data type is deemed approximately unbiased. 
    {\it Middle:} Same as left, but restricted to wavenumber ($k$) values where the low resolution 
    runs are approximately unbiased.
    {\it Right:} Same as middle, but with estimated posterior mean subtracted.}
    \label{fig:plot_data}
\end{figure}

These spectra are represented as a function of wavenumber $k$.  Following 
\cite{moran2023mira}, we model on the emulation space 
$\mathcal{P}(k)=\log_{10}\left(\frac{k^{1.5}P(k)}{2\pi^2}\right)$, where $P(k)$ represents the
original spectra. Output is available for $n=351$ values of $k$, spanning
$0.001 \leq k \leq 5$, but each data type has unique wavenumber ranges
where it is deemed approximately unbiased. For $k<0.04$, only $y_p$ provides a reliable 
estimate of the true spectra. $y_{\ell_r}$ are valid for $0.04 \leq k \leq 0.25$, and 
$y_h$ is valid for $0.04 \leq k \leq 5$.  Figure \ref{fig:plot_data} shows an example 
of the output for a particular cosmology. When we focus on $k$ values where $y_{\ell_r}$ 
is valid (center panel), we see each low-resolution and the high-resolution run oscillate around 
a mean term, which is relatively smooth, compared to these realizations. When this
mean term is subtracted, we will obtain a plot like the right panel in 
Figure \ref{fig:plot_data}.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{CAMB_fit_model1.png}
    \caption{Example of DGP.HM model fit for the first batch of model runs from the CAMB data, 
             with LOESS mean term subtracted. We can compare the orange lines 
             (posterior mean and dotted 95\% credible interval) to the light blue line,
             representing the infinite-resolution ``true" spectrum.}   
    \label{fig:fit_camb}
\end{figure}
